Millions of Type Errors

### 2023-05-15 oopsla23/paper.tex
fig 1: full-size anon version
recolor fit lines, red=fs green=te

\begin{figure}
  \anon{
    \includegraphics[width=.45\textwidth]{img/roblox-studio.png}
    \includegraphics[width=.45\textwidth]{img/roblox-studio-ide.png}
  }
  \caption{\anon{Roblox Studio 3D creation} tools (left) and IDE (right)}
  \label{fig:roblox-studio}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=0.8\columnwidth]{img/fit-nocheck-Force.pdf}
  \includegraphics[width=0.8\columnwidth]{img/fit-nonstrict-TypeE.pdf}
  \includegraphics[width=0.8\columnwidth]{img/fit-strict-TypeE.pdf}
  \caption{Best-fit curves for errors in each mode (\code{fs} for \mnocheck{}, \code{te} for the others)}
  \label{f:scribbles}
\end{figure}

>>>>

\begin{figure}

  \makeatletter
  \if@ACM@anonymous
    \includegraphics[width=.45\textwidth]{img/anon-studio.png}
    \includegraphics[width=.45\textwidth]{img/anon-studio-ide.png}
  \else
    \includegraphics[width=.45\textwidth]{img/roblox-studio.png}
    \includegraphics[width=.45\textwidth]{img/roblox-studio-ide.png}
  \fi
  \makeatother

  \caption{\anon{Roblox Studio 3D creation} tools (left) and IDE (right)}
  \label{fig:roblox-studio}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=0.8\columnwidth]{img/fit-nocheck-Force-3.pdf}
  \includegraphics[width=0.8\columnwidth]{img/fit-nonstrict-TypeE-3.pdf}
  \includegraphics[width=0.8\columnwidth]{img/fit-strict-TypeE-3.pdf}
  \caption{Best-fit curves for errors in each mode (\code{fs} for \mnocheck{}, \code{te} for the others)}
  \label{f:scribbles}
\end{figure}
